### 2019-04-07 thesis_proposal_LaTeX/Chapters/6_StateoftheArt.tex
new state of the art

>>>>

Figure \ref{fig:SerieAflowCurve} shows evidence that the equal increase of PEO and TBATFB concentrations result in an increase of shear viscosity rate $\gamma$. for concentrations from 1.00 to 0.25 $w t \%$, a slight increase of flow curve strain $\eta$ for low shear rates to 0.3 $s^{-1}$. For shear rates greater than 0.3 $s^{-1}$, the $\eta$ starts to decrease, as the polymer entanglements start to break apart, reducing friction between the polymer threads and therefore the viscosity also is reduced. The solution samples show a Newtonian-like behaviour and that may be caused by the use of the solvent cyclopentanone and by the small sized SU-8 2002 molecules.

\begin{figure}[th]
\centering
\includegraphics[width=0.75\textwidth]{./Figures/SerieAflowCurve.png}
\decoRule
\caption[Serie A - Flow curve]{Serie A - Flow curve}
\label{fig:SerieAflowCurve}
\end{figure}

From the results in Figure \ref{fig:SerieAflowCurve}, it is noticeable that the addition of small amounts of PEO and TBATFB cause a change of one order of magnitude in shear viscosity in small concentration and a triple change in high concentrations.

Series B flow curve results (Figure \ref{fig:SerieBflowCurve}) do not show a clear correlation between PEO concentrations and shear viscosity. For PEO of 1 $w t \%$, a slow increase in $\eta$ is present with the increase of shear rate, after $\gamma$ drops from 2 to 0.8 $Pa s$, a shear thinning behaviour is present. For 0.50 and 0.75 $w t \%$ concentrations, a shear thinning behaviour is present throughout the plot. For the 0.50 $w t \%$ sample, viscosity value varied between 0.2 and 0.4 $Pa s$; and between 0.5 and 2.0 $Pa s$ for the 0.75 $w t \%$ sample. Viscosity is stabilized at 0.1 $Pa s$ when the shear rate is between 1 and 20 \% for the sample of PEO $w t \%$. After stabilization, the viscosity decreases from 0.1 to 0.02 $Pa s$ for shear rates between 20 to 100 $s^{-1}$. For PEO 0.00 $w t \%$, a high variation is present in viscosity readings due to the presence of electrolytes cause amendments in the polymer chain within the solution.

\begin{figure}[th]
\centering
\includegraphics[width=0.75\textwidth]{./Figures/SerieBflowCurve.png}
\decoRule
\caption[Serie B - Flow curve]{Serie B - Flow curve}
\label{fig:SerieBflowCurve}
\end{figure}
